\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and Parallel-Jaw Grasps and a Multi-Armed Bandit Algorithm with Correlated Rewards for Robust Grasp Planning at Scale \versionline{7}

### 2015-09-14 ICRA2016/bandits_docs/includes/dataset.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

\TODO{Make this flow with above paragraph!}
The Dexterity Network (Dex-Net) 1.0, is a dataset of prior 3D object models annotated with parallel-jaw grasps and a similarity metric to efficiently index objects.
Dex-Net consists of over 10,000 3D mesh models, selected to represent objects that might be encountered in warehousing or the home such as tableware, tools, and toys.
%Laser-scanned models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} constitute 355 of the total models.
%The majority of Dex-Net is synthetic 3D mesh models from 3DNet\cite{wohlkinger20123dnet}, a benchmark for object detection in robotics research,  ModelNet~\cite{wu20143d}, a benchmark for 3D model classification, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}, a competition benchmark with many categories to test the state-of-the-art in shape retrieval annually.
\figref{datasets} details the data sources and their sizes.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.1]{figures/dataset_table.jpg}
\caption{The seven datasets used in Dex-Net 1.0 with information on whether or not the models were laser-scanned, the number of models in the dataset, and the number of labelled categories (if category labels are present).}
\figlabel{datasets}
\vspace*{-15pt}
\end{figure}

\subsection{Data Cleaning}
Each object in Dex-Net is originally specified as a 3D mesh $\mX = \{\mV, \mT\}$ where $\mV = \{\bv_1, ..., \bv_V\}$ is a set of $V$ vertices such that $\bv_i \in \bR^3$ for $i = 1, ..., V$ and $\mT = \{t_1, ..., t_F\}$  is a set of $F$ triangles such that $t_j \in \mathbb{Z}_{+}^3$ for $j = 1, ..., F$.
We preprocess each model by first removing unreferenced vertices and degenerate triangles.
Next, we compute the object reference frame by performing Principal Component Analysis (PCA) on the vertices of the mesh and aligning the $z$-axis with the first principal component and the $y$-axis with the second principal component
We then set the object center of mass $\bz$ to be the center of the bounding box for the reoriented mesh.
Since synthetic models may not be specified in meters, we also rescale each mesh such that the smallest dimension of the bounding box lies within $w = 0.1m$, which is approximately the maximal opening width of a PR2 gripper.
Finally, we convert each mesh to a signed distance field $f$ using SDFGen~\cite{sdfgen}, an open-source C++ tool.

\subsection{Grasp Sampling}
\seclabel{grasp-sampling}
Each 3D object $\mO_i$ in Dex-Net is labelled with up to 250 parallel-jaw grasps and the $P_F$ for each.
We generate candidate grasps using a modified version of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
Let $w$ be the maximal opening of the gripper, $\hat{\gamma}$ be a sampled friction coefficient, and $\mS $ be the set of points on the object surface for an SDF $f$ as described in \secref{grasp-param}.
To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mC$ using rejection sampling.
Next we sample a direction $\bv \in \bS^2$ uniformly at random from the cone and compute:
%\vspace{-2ex}
\begin{align*}
	\bc_2 = \bc_1 + (w / 2 - t_2^*) \bv  &&  \bx = 0.5 (\bc_1 + \bc_2)
\end{align*}
\noindent where $t_2^*$ is defined in \secref{contact}.
This yields a grasp $\bg_{i,k} = (\bx, \bv)$.
We add $\bg_{i,k}$ to our candidate set if both $\bv^T \bn_1 \leq \cos(\arctan(\hat{\gamma}))$ and $\bv^T \bn_2 \leq \cos(\arctan(\hat{\gamma}))$.

@@

\subsection{Object Similarity Embedding}
\seclabel{object-similarity}
In order to efficiently index prior 3D object and grasp data from Dex-Net, we embed each object in a Euclidean feature space in which similar objects are close together.
Our similarity embedding is based on multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape retrieval that uses the powerful features leared by CNNs on millions of images~\cite{krizhevsky2012imagenet}.

\figref{global-feature-model} illustrates our method.
Let $R$ be the maximum dimension of the object bounding box.
We first render every object on a white background in a total of $N_c = 50$ virtual camera views oriented toward the object center and discretized on a viewing sphere along angle increments $\delta_{\theta} = \frac{4 \pi}{N_c}$ and $\delta_{\phi} = \frac{2 \pi}{N_c}$ and radii $r = R, 2R$.
Then we train a CNN with the architecture of AlexNet~\cite{krizhevsky2012imagenet} to predict the 3D object class label for the rendered images on a training set of models. 
We initialize the weights of our network with the weights learned on ImageNet by Krizhevsky et al.~\cite{krizhevsky2012imagenet} and optimize using Stochastic Gradient Descent (SGD). 
Next, we pass each of the $N_c$ views of each object through the optimized CNN and max-pool the output of the fc7 layer, the highest layer of the network before the class label prediction. 
Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output to from 4028 dimensions to 100 dimensions.
This yields our representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object.
Our method differs from the MV-CNN of Su et al.~\cite{su2015multi} because we use PCA for the final output, while Su et al. use a second CNN on the output of the pooled views.

@@

%In our implementation, we trained our MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD, and the final PCA step captured approximately 85\% of the variance of the vectors.
%The image classification training step had a test accuracy of 76\%.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.3]{figures/illustrations/cnn_model.png}
\caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty. We pass a set of 50 virtually rendered camera viewpoints discretized around a sphere through a deep Convolutional Neural Network (CNN) with the AlexNet~\cite{krizhevsky2012imagenet} architecture. Finally, we take the maximum fc7 response across each of the 50 views for each dimension and run PCA to reduce the dimensionality of the output.}
\figlabel{global-feature-model}
\vspace*{-15pt}
\end{figure}

>>>>

%\TODO{Perhaps a cleaner transition here}
We now extend robust grasp planning to leverage prior data from a set of objects by introducing the Dexterity Network (Dex-Net) 1.0, a growing dataset of over 10,000 prior 3D object models annotated with parallel-jaw grasps and a similarity metric to efficiently index objects.
The dataset is selected to represent objects that might be encountered in warehousing or the home such as containers, tools, tableware, and toys.
%Laser-scanned models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} constitute 355 of the total models.
%The majority of Dex-Net is synthetic 3D mesh models from 3DNet\cite{wohlkinger20123dnet}, a benchmark for object detection in robotics research,  ModelNet~\cite{wu20143d}, a benchmark for 3D model classification, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}, a competition benchmark with many categories to test the state-of-the-art in shape retrieval annually.
\tabref{datasets} details the data sources and their sizes.

{%
\setlength{\tabcolsep}{1pt}

\begin{table}[t]
\centering
        \begin{tabular}{L{2.5cm} || R{1.5cm} | R{1.5cm}}
        \multicolumn{1}{c ||}{\specialcell{\bf Dataset}} & \multicolumn{1}{c |}{\specialcell{\bf \# Models}}  & \multicolumn{1}{c}{\specialcell{\bf Synthetic?}} \\
        \hline & & \\ [-1.5ex]
        SHREC2014~\cite{li2015comparison} & 8,987 & Y\\
        ModelNet40~\cite{wu20153d} & $^*$2,539 & Y \\
        3DNet~\cite{wohlkinger20123dnet} & 1,371 & Y \\
        KIT~\cite{kasper2012kit} & 129 & N \\
        BigBIRD~\cite{singh2014bigbird} & 120 & N \\
        YCB~\cite{calli2015benchmarking} & 80 &  N\\
        APC & 26 & N\\
        \hline & & \\ [-1.5ex]
        {\bf Total} & 13,252 & \\ 
        \end{tabular}
        \caption{The seven datasets used in Dex-Net 1.0 with the number of models in the dataset and whether or not the models were laser-scanned. $^*$ indicates a subset of the original dataset. }
		\tablabel{datasets}
\vspace*{-15pt}
\end{table}
}

%\begin{figure}[t!]
%\centering
%\includegraphics[scale=0.1]{figures/dataset_table.jpg}
%\caption{\TODO{Remove columns}}
%\figlabel{datasets}
%\vspace*{-15pt}
%\end{figure}

\subsection{Data Cleaning}
Each object in Dex-Net is specified as a 3D mesh $\mX = \{\mV, \mT\}$ where $\mV = \{\bv_1, ..., \bv_V\}$ is a set of $V$ vertices such that $\bv_i \in \bR^3$ for $i = 1, ..., V$ and $\mT = \{t_1, ..., t_F\}$  is a set of $F$ triangles such that $t_j \in \mathbb{Z}_{+}^3$ for $j = 1, ..., F$.
We preprocess each model by first removing unreferenced vertices and degenerate triangles.
Next, we compute the object reference frame by performing Principal Component Analysis (PCA) on the vertices of the mesh and aligning the $z$-axis with the first principal component and the $y$-axis with the second principal component
We then set the object center of mass $\bz$ to be the center of the bounding box for the reoriented mesh.
Since synthetic models may not be specified in meters, we also rescale each mesh such that the smallest dimension of the bounding box lies within $w = 0.1m$, which is approximately the maximal opening width of a PR2 gripper.
Finally, we convert each mesh to an SDF using SDFGen~\cite{sdfgen}, an open-source C++ tool.

\subsection{Grasp Sampling}
\seclabel{grasp-sampling}
Each 3D object $\mO_i$ in Dex-Net is labelled with up to 250 parallel-jaw grasps and the $P_F$ for each.
We generate $N_g$ grasps for each object using a modification of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
Let $w$ be the maximal opening of the gripper, $\hat{\gamma}$ be a sampled friction coefficient, and $\mS$ be the set of points on the object surface for an SDF $f$ as described in \secref{grasp-param}.
To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mS$ using rejection sampling.
Next we sample a direction $\bv \in \bS^2$ uniformly at random from the friction cone and compute:
%\vspace{-2ex}
\begin{align*}
	\bc_2 = \bc_1 + (w / 2 - t_2^*) \bv  &&  \bx = 0.5 (\bc_1 + \bc_2)
\end{align*}
\noindent where $t_2^*$ is defined in \secref{contact}.
This yields a grasp $\bg_{i,k} = (\bx, \bv)$.
We add $\bg_{i,k}$ to our candidate set if the contacts are antipodal~\cite{mahler2015gp}, or $\bv^T \bn_1 \leq \cos(\arctan(\hat{\gamma}))$ and $\bv^T \bn_2 \leq \cos(\arctan(\hat{\gamma}))$.

@@

\subsection{Grasp Differential Heightmap Features}
\seclabel{grasp-similarity}
To measure grasp similarity, we also embed each parallel-jaw grasp $\bg$ on object $\mO$ in Dex-Net in a feature space based on 2D projections of the local surface orientation, a variant of grasp heightmaps~\cite{herzog2012template, kappler2015leveraging}.
Let $d_h \in \mathbb{Z}$ be a number of pixels for the projection, let $\mP = \{-d_h, ..., d_h\}$ be row / column pixel indices, let $\delta \in \mathbb{R}$ be the pixel resolution in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
Our heightmap at contact $i$, $\bh_{i}: \mP \times \mP \rightarrow \bR$, maps discrete locations along the tangent plane specified by $\bt_1, \bt_2$ to the distance to the surface along the grasp axis $\bv$.
To compute the heightmap value at pixel $u,v \in \mP$, we first compute the 3D location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$.
Then we assign
\begin{align*}
	\bh_i(u,v) = \minimum{t \geq -r} t \text{ such that } f\left( \bp_i(u,v) + (-1)^{i} \bv \right) = 0
\end{align*}
\noindent where $f$ is the SDF of object $\mO$. 
We then make $\bh_i$ rotation-invariant by orienting its axes to align with the eigenvectors of the weighted covariance matrix of the 3D surface points that generate the heightmap as described in~\cite{tombariunique}.
\figref{local-feature-model} illustrates local surface patches extracted by this procedure.
Since force closure depends largely on object surface normals at the contact points, we finally take the $x$- and $y$-image gradients of $\bh_i$ to form differential heightmaps $\bd_{i,x}$ and $\bd_{i,y}$.
Our full feature vector for the grasp-object pair is $\eta(\bg, \mO) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$, which we store for each grasp in Dex-Net.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.325]{figures/illustrations/local_feature_model.eps}
\caption{Illustration of three local surface heightmaps extracted on a teapot. Each heightmap is ``rendered" along the grasp axis at each contact point and oriented by the local directions of maximum variation in the heightmap.  We extract the gradients of these heightmaps to measure similiarity between grasps in Dex-Net.}
\figlabel{local-feature-model}
\vspace*{-15pt}
\end{figure}

\section{Deep Learning for Object Similarity}
\seclabel{object-similarity}
In order to efficiently index prior 3D object and grasp data from Dex-Net, we embed each object in a Euclidean vector space in which similar objects will be close together.
We use multi-view Convolutional Neural Networks (MV-CNNs)~\cite{aubry2015understanding, su2015multi}, a new method for 3D shape classification that outperforms the accuracy of previous methods by over 10\% on the ModelNet40 shape classification benchmark and uses the powerful features learned by CNNs on millions of images~\cite{krizhevsky2012imagenet}.

\figref{global-feature-model} illustrates the approach.
Let $R$ be the maximum dimension of the object bounding box.
We first render every object on a white background in a total of $N_c = 50$ virtual camera views oriented toward the object center and discretized on a viewing sphere along angle increments $\delta_{\theta} = \frac{4 \pi}{N_c}$ and $\delta_{\phi} = \frac{2 \pi}{N_c}$ and radii $r = R, 2R$.
Then we train a CNN with the architecture of AlexNet~\cite{krizhevsky2012imagenet} to predict the 3D object class label for the rendered images on a training set of models. 
We initialize the weights of our network with the weights learned on ImageNet by Krizhevsky et al.~\cite{krizhevsky2012imagenet} and optimize using Stochastic Gradient Descent (SGD). 
Next, we pass each of the $N_c$ views of each object through the optimized CNN and max-pool the output of the fc7 layer, the highest layer of the network before the class label prediction. 
Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output from 4028 dimensions to 100 dimensions.
This yields our representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object.
%Our method differs from the MV-CNN of Su et al.~\cite{su2015multi} because we use PCA for the final output, while Su et al. use a second CNN on the output of the pooled views.

@@

In our implementation, we trained our MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD.
The final PCA step captured approximately 85\% of the variance of the vectors.
The image classification training step had a test accuracy of 76\%.
To validate our implementation, we tested our method on the SHREC 2014 challenge dataset and achieved a 1-NN accuracy of 86.7\%, compared to 86.8\% achieved by the winner of SHREC 2014~\cite{li2015comparison}.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.25]{figures/illustrations/cnn_model.eps}
\caption{Illustration of our method for embedding 3D object models in a Euclidean vector space for computing global shape similiarty. We pass a set of 50 virtually rendered camera viewpoints discretized around a sphere through a deep Convolutional Neural Network (CNN) with the AlexNet~\cite{krizhevsky2012imagenet} architecture. Finally, we take the maximum fc7 response across each of the 50 views for each dimension and run PCA to reduce the dimensionality of the output.}
\figlabel{global-feature-model}
\vspace*{-15pt}
\end{figure}

### 2015-09-14 ICRA2016/bandits_docs/includes/experiments.tex
Long version of the paper is now near-finished. From this point on I will work on trimming

\section{Experiments}
\seclabel{experiments}
\TODO{Add average convergence experiment with test set}
\TODO{Add sensitivity to uncertainty}

We evaluated the convergence rate of Algorithm~\ref{alg:full} for varying sizes of prior data used from Dex-Net and examined the sensitivity of the convergence rate to object shape, the similarity kernel bandwidths, and uncertainty.
We created three nested training sets of 100, 1000, and 10000 objects by uniformly sampling objects from Dex-Net.
From the remaining objects we created a set of 20 validation objects for selecting algorithm hyperparameters and a set of 30 objects for test data.
We ran our algorithm with $N_n = 10$ nearest neighbors.
We also used isotropic covariance with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.

The bandwidths of our similarity kernel were constrained to be disgonal for the grasp parameters features $C_g = \Lambda$, isotropic for the global shape features $C_s = \sigma I$ for $\sigma \in \bR$, and a gaussian mask $C_d$ centered on the gradient heightmaps with height $w_d \in \bR$ and variance $\sigma_d \in \bR$.
The bandwidths were selected by maximizing average convergence rate on the validation set using a grid search over hyperparameters.

To handle the scale of the experiments, we developed a Cloud-based software library on top of Google Cloud Platform.
We used Google Compute Engine to distribute trials of MAB algorithms across objects and Google Cloud Storage (GCS) to store Dex-Net.
Our experimental scripts launched up to 1500 GCE single core instances at one time for hyperparameter tuning and convergence analysis, reducing the runtime of our experiments by over $1000\times$.

\subsection{Scaling of Average Convergence Rate}
\TODO{Replace with test results. Current are on validation set due to time constraints}
\TODO{Add 100 model results}

To examine the effects of orders of magnitude of prior data on convergence to a grasp with high $P_F$, we ran Algorithm~\ref{alg:full} on the 20 validation objects with priors computed from 1,000 and 10,000 objects from Dex-Net. 
~\figref{avg-reward} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for each of the 20 validation objects for 4,000 iterations.
The plot also compares Algorithm~\ref{alg:full} to uncorrelated Thompson sampling and uniform allocation~\cite{laskey2015bandits}.
Our algorithm with 10,000 objects takes approximately $3.5\times$ fewer iterations to reach the maximum normalized $P_F$ value reached by Thompson sampling over all iterations.
Furthermore, the 10,000 object curve does not reach below 90\% of the best grasp in the set across all iterations, suggesting that a grasp with high $P_F$ is found using prior data alone.
However, we see that on average our algorithm makes progress more slowly than Thompson sampling.

@@

\subsection{Sensitivity to Object Shape}
\seclabel{shape-sens}
To understand the behavior of Algorithm~\ref{alg:full} on individual 3D objects, we examined the convergnce rate with a 3D model of the only drill in Dex-Net and a spray bottle, which is an uncommon object category but has a few examples in Dex-Net.
~\figref{avg-reward-obj} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for 4,000 iterations on these two objects.
We see that the spray bottle converges very quickly when using a prior dataset of 10,000 objects, finding the optimal grasp in the set in about 1,500 iterations.
\figref{spray-grasps} illustrates the grasps predicted to have the highest $P_F$ on the spray bottle by the algorithms about 100 iterations.
However, performance on the drill does not increase using either 1,000 or 10,000 objects.

This behavior may be explained by the similarity of the closest nearest neighbors in Dex-Net found by our shape similiarty MV-CNN, displayed in \figref{query}.
We see that the spray bottle has no nearest neighbors that are very close in shape in the 1,000 object dataset, but in the 10,000 object dataset two nearly identical spray bottles are retrieved.
On the other hand, the drill has no similar neighbors in either dataset, and the closest model in all of Dex-Net according to our similarity metric is a phone.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.31]{figures/illustrations/avg_reward_drill.eps}
\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net on a spray bottle (top) and drill (bottom). We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation. (Top) For the spray bottle, Algorithm~\ref{alg:full} does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimizal grasp once 10,000 objects are used. (Bottom) The drill, which is relatively rare in the dataset, has no noticeable performance increase over Thompson sampling, even with 10,000 objects.}
\figlabel{avg-reward-obj}
\vspace*{-15pt}
\end{figure}

@@

\section{Sensitivity to Similarity Kernel Bandwidth}
\seclabel{band-sens}
We also studied the sensitivity of our algorithm to the kernel bandwidth hyperparameters described in \secref{features}.
We varied the bandwidth of the kernel for the heightmap gradients to the higher value $1 / 350$ and the lower value $1 / 450$ , as this was the most discriminative feature maps found by our hyperparameter tuning.
\figref{bandwidth-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 20 validation objects.
We see that increasing the bandwidth of the kernel can drastically affect the performance of the algorithm, causing the performance to be no better than uniform allocation.
This may be because overestimating similarities can lead to a grasp with high $P_F$ being predicted too low, or vice versa.
One the other hand, decreasing the bandwidth also decreases the convergence rate but Algorithm~\ref{alg:full} with 10,000 prior objects still outperforms Thompson sampling.
This suggests that a conservative setting of similiarity kernel bandwidth may be preferable for Algorithm~\ref{alg:full}.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.23]{figures/illustrations/weight_sensitivity.eps}
\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right). We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation. (Left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocatoin. (Bottom) A lower kernel bandwith decreases the convergence rate, but Algorithm~\ref{alg:full} still selects a grasp within 85\% of the grasp with highest $P_F$ for all iterations, on average.}
\figlabel{bandwidth-sens}
\vspace*{-15pt}
\end{figure}

\section{Sensitivity to Uncertainty}
\TODO{Write section}

>>>>

\section{Experiments}
\seclabel{experiments}

\TODO{Update results with any experiments. The current section basically reflects what we should expect but I'm running a few with slightly more test objects to see what happens}

We evaluate the convergence rate of the Dex-Net 1.0 algorithm for varying sizes of prior data used from Dex-Net and explore the sensitivity of the convergence rate to object shape, the similarity kernel bandwidths, and uncertainty.
We created two training sets of 1000, and 10000 objects by uniformly sampling objects from Dex-Net.
From the remaining objects, we created a set of 300 validation objects for selecting algorithm hyperparameters and a set of 45 test objects.
We ran our algorithm with $N_n = 10$ nearest neighbors and used isotropic uncertainty with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.

The bandwidths of our similarity kernel were constrained to be diagonal for the grasp parameters features $C_g = \Lambda$, isotropic for the global shape features $C_s = \sigma I$ for $\sigma \in \bR$, and a Gaussian mask $C_d$ centered on the differential heightmaps with height $w_d \in \bR$ and variance $\sigma_d \in \bR$.
The bandwidths were selected by maximizing the log likelihood of the true $P_F$ under the CCBP model on the validation set using a grid search over hyperparameters.

To scale the experiments, we developed a Cloud-based software library on top of Google Cloud Platform.
We used Google Compute Engine (GCE) to distribute trials of MAB algorithms across objects and Google Cloud Storage to store Dex-Net.
Our experimental scripts launched up to 1500 GCE single core instances at one time for hyperparameter tuning and convergence analysis, reducing the runtime of our experiments by over $1000\times$.

\subsection{Scaling of Average Convergence Rate}

To examine the effects of orders of magnitude of prior data on convergence to a grasp with high $P_F$, we ran Algorithm~\ref{alg:full} on the 20 validation objects with priors computed from 1,000 and 10,000 objects from Dex-Net. 
~\figref{avg-reward} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for each of the 20 validation objects for 4,000 iterations.
The plot also compares Algorithm~\ref{alg:full} to uncorrelated Thompson sampling and uniform allocation~\cite{laskey2015bandits}.
Our algorithm with 10,000 objects takes approximately $3.5\times$ fewer iterations to reach the maximum normalized $P_F$ value reached by Thompson sampling over all iterations.
Furthermore, the 10,000 object curve does not fall below 90\% of the best grasp in the set across all iterations, suggesting that a grasp with high $P_F$ is found using prior data alone.
%However, we see that on average our algorithm makes progress more slowly than Thompson sampling.

@@

\subsection{Sensitivity to Object Shape}
\seclabel{shape-sens}
To understand the behavior of Algorithm~\ref{alg:full} on individual 3D objects, we examined the convergnce rate with a 3D model of the only drill in Dex-Net and a spray bottle, which is an uncommon object category but has a few examples in Dex-Net.
~\figref{avg-reward-obj} shows the normalized $P_F$ (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for 4,000 iterations on these two objects.
We see that the spray bottle converges very quickly when using a prior dataset of 10,000 objects, finding the optimal grasp in the set in about 1,500 iterations.
\figref{spray-grasps} illustrates the grasps predicted to have the highest $P_F$ on the spray bottle by the different algorithms after 100 iterations.
However, performance on the drill does not increase using either 1,000 or 10,000 objects.

This suggests the value of the Dex-Net objects found by our shape similiarty MV-CNN, displayed in \figref{query}.
We see that the spray bottle has no nearest neighbors that are very close in shape in the 1,000 object dataset, but in the 10,000 object dataset two nearly identical spray bottles are retrieved.
On the other hand, the drill has no similar neighbors in either dataset, and the closest model in all of Dex-Net according to our similarity metric is a phone.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.31]{figures/illustrations/avg_reward_drill.eps}
\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net on a spray bottle (top) and drill (bottom). We measure quality by the $P_F$ for the best grasp predicted by the algorithm on each iteration and compare with uncorrelated Thompson sampling and uniform allocation. (Top) For the spray bottle, Algorithm~\ref{alg:full} does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimial grasp once 10,000 objects are used. (Bottom) The drill, which is relatively rare in the dataset, has no noticeable performance increase over Thompson sampling, even with 10,000 objects.}
\figlabel{avg-reward-obj}
\vspace*{-15pt}
\end{figure}

@@

\section{Sensitivity to Similarity Kernel Bandwidth}
\seclabel{band-sens}
We also studied the sensitivity of our algorithm to the kernel bandwidth hyperparameters described in \secref{ccbps}.
We varied the bandwidth of the kernel for the heightmap gradients to the higher value $1 / 350$ and the lower value $1 / 450$ , as this was the most discriminative feature maps found by our hyperparameter tuning.
\figref{bandwidth-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 20 validation objects.
We see that increasing the bandwidth of the kernel can reduce performance to be on par with uniform allocation.
This may be because overestimating similarities can lead to a grasp with high $P_F$ being predicted too low, or vice versa.
One the other hand, decreasing the bandwidth also decreases the convergence rate but Algorithm~\ref{alg:full} with 10,000 prior objects still outperforms Thompson sampling.
This suggests that a conservative setting of similiarity kernel bandwidth is important.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.23]{figures/illustrations/weight_sensitivity.eps}
\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right). (Left) Using a higher kernel bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation. (Bottom) A lower kernel bandwith decreases the convergence rate, but Algorithm~\ref{alg:full} still selects a grasp within 85\% of the grasp with highest $P_F$ for all iterations, on average.}
\figlabel{bandwidth-sens}
\vspace*{-10pt}
\end{figure}

\section{Sensitivity to Pose and Friction Uncertainty}
\seclabel{u-sens}
We also studied the sensitivity of our algorithm to the levels of object pose, gripper pose, and friction coefficient uncertainty for the test object.
We tested low uncertainty with object and gripper translation variance $\sigma_{t} = 0.0025$, object and gripper rotation variance $\sigma_{r} = 0.05$, and friction variance $\sigma_{\gamma} = 0.05$ as well as high variance $\sigma_{t} = 0.01, \sigma_{r} = 0.2,$ and $\sigma_{\gamma} = 0.2$.
The uncertainty levels used to label grasps in Dex-Net were not changed.
\figref{u-sens} shows the normalized $P_F$ versus iteration averaged over 25 trials for 4,000 iterations on the 45 test objects.
The normalized $P_F$ for increases and descreases across all methods for low and high uncertainty, respectively.
Also, prior data no longer increases convergence rate but a mismatch between the uncertainty on the test object and training objects does not cause performance to decrease below Thompson sampling without priors.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.23]{figures/illustrations/u_sensitivity.eps}
\caption{Average normalized grasp quality versus iteration over 25 trials per object for our algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net with low uncertainty (left) $\sigma_{t} = 0.0025, \sigma_{r} = 0.05, \sigma_{\gamma} = 0.05$ and high uncertainty (right) $\sigma_{t} = 0.01, \sigma_{r} = 0.2, \sigma_{\gamma} = 0.2$ on the test set. Lower uncertainty increases the quality for all methods and higher uncertainty decreases the quality for all methods. Interestingly, in both cases prior data has little effect but the convergence rate is still on par with Thompson sampling with no prior data.}
\figlabel{u-sens}
\vspace*{-10pt}
\end{figure}
